---
title: "CURC analysis"
author: "Collin Farrell"
date: "4/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_knit$set(options(digits = 4))
knitr::opts_chunk$set(fig.align = "center") 
```

```{r}
library(magrittr)
library(tidyverse)
library(latex2exp)
```


## Gonad Energy Density

```{r}
gonad_dry <- read_csv("gonad_dry.csv")

gonad_ed <- read_csv("gonad_ed.csv")
  
gonad_group <- read_csv("gonad_grouped.csv") %>%
  filter(percent_DM < 0.40)
```

Below I plotted the relationship between energy density (calorimetry) and % dry matter for females of known ploidy captured at Narraguinnep. Pretty clear seperation here with the exception of a possible triploid outlier, need to check about this point.

```{r}
ggplot(gonad_group, aes(y = mean_ED, x = percent_DM*100))+
  geom_point(aes(color = ploidy), size = 4)+
  geom_smooth(method = "lm", color = "black")+
  labs(x = "Dry Matter Content (%)", y = "Mean Energy Density (J/g wet mass)", color = "Ploidy")+
  theme_classic()+
  theme(text = element_text(size = 28))
```

The $R^2$ for the log-log regression on energy density ~ % dry matter is 0.9902! The equation for this relationship is:

$$ED_{gonad} = 28.11 \times DM^{1.108} $$
where $ED_{gonad}$ is gonad energy density (MJ/kg WW), and DM is gonad dry matter content (%).

```{r}
summary(lm(log(mean_ED)~ log(percent_DM), data = gonad_group))
```

Below show boxplots comparing triploid and diploid females and associated summary statistics:

```{r}
ggplot(gonad_group, aes(y = mean_ED, x = ploidy, fill = ploidy))+
  geom_boxplot()+
  labs(x = "Ploidy)", y = "Mean Energy Density (kJ/g wet mass)")+
  theme_classic()
```

```{r}
gonad_group %>%
  group_by(ploidy) %>%
  summarize(n = n(),
            'Mean Energy Density' = mean(mean_ED),
            'SD Energy Density' = sd(mean_ED)) %>%
  kable()
```