---
title: "CURC analysis"
author: "Collin Farrell"
date: "4/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_knit$set(options(digits = 4))
knitr::opts_chunk$set(fig.align = "center") 
```

```{r}
library(magrittr)
library(tidyverse)
library(latex2exp)
library(nlme)
library(emmeans)
library(MuMIn)
```


## Gonad Energy Density

```{r}
gonad_dry <- read_csv("gonad_dry.csv")

gonad_ed <- read_csv("gonad_ed.csv") %>% 
    filter(percent_DM < 0.40) %>% #removes possible triploid outlier
  mutate(development = ifelse(goncond == 3, "Mature", ifelse(goncond == 2, "Developing", "Immature"))) %>%
  mutate(development = fct_relevel(development,c("Immature","Developing", "Mature")))
  
gonad_group <- read_csv("gonad_grouped.csv") %>%
  filter(percent_DM < 0.40) %>% #removes possible triploid outlier
  mutate(development = ifelse(goncond == 3, "Mature", ifelse(goncond == 2, "Developing", "Immature"))) %>%
  mutate(development = fct_relevel(development,c("Immature","Developing", "Mature")))
```

# Comparing Maturity Levels

```{r include=FALSE}
lme1 <- lmerTest::lmer(ED_ww ~ development+(1|fishid), data = gonad_ed) #mixed-effects ANOVA
summary(lme1)
```

```{r include=FALSE}
emmeans(lme1,pairwise~development) #pairwise comparisons
```

```{r}
ggplot(gonad_group, aes(y = mean_ED, x = development))+
  geom_boxplot(aes(fill = development), color = "grey50")+
  labs(x = "Developmental Stage", y = "Mean Energy Density (J/g wet mass)", color = "Development")+
  theme_classic()+
  geom_hline(yintercept = 2.41, lty = "dashed")+
  theme(text = element_text(size = 28))+
  scale_fill_manual(name = "Development",
                     labels = c("Immature","Developing","Mature"),
                     values = c("#FAB45A","#AEB4C2","#262B30"))+
    theme(text = element_text(size = 28))
    
```

## Linear Mixed Model

```{r}
lme2 <- lmerTest::lmer(log(ED_ww)~log(percent_DM) + (log(percent_DM)|fishid),data= gonad_ed)
summary(lme2)
```

```{r}
r.squaredGLMM(lme2)
```

Below I plotted the relationship between energy density (calorimetry) and % dry matter for females of known ploidy captured at Narraguinnep. 

The marginal $R^2$ for the log-log regression on energy density ~ % dry matter is 0.9816, the conditional $R^2$ was 0.9989! The equation for this relationship is:

$$ED_{gonad} = 31.71 \times DM^{1.171} $$
where $ED_{gonad}$ is gonad energy density (MJ/kg WW), and DM is gonad dry matter content (%).

```{r}
ci<- confint(lme2) 

ci %<>% as_tibble()

lwr_a <- ci[5,1]
upr_a <- ci[5,2]

lwr_b <- ci[6,1]
upr_b <- ci[6,2]

preddata <- tibble(percent_DM = seq(0,0.5, by = 0.001))

preddata %<>% mutate(ED_ww = exp(fixef(lme2)[1])*percent_DM^fixef(lme2)[2])

predupr <- tibble(percent_DM = seq(0,0.5, by = 0.001))

predupr %<>%mutate(ED_ww = exp(upr_a[[1]])*percent_DM^upr_b[[1]])

predlwr <- tibble(percent_DM = seq(0,0.5, by = 0.001))

predlwr %<>%mutate(ED_ww = exp(lwr_a[[1]])*percent_DM^lwr_b[[1]])

ggplot(gonad_ed, aes(y = ED_ww, x = percent_DM*100))+
  geom_point(aes(color = development, shape = development), size = 4)+
  geom_line(data=preddata)+
  geom_line(data=predupr, lty = "dashed")+
  geom_line(data =predlwr, lty = "dashed")+
  labs(x = "Dry Matter Content (%)", y = "Energy Density (J/g wet mass)", color = "Development")+
  theme_classic()+
  theme(text = element_text(size = 28))+
  scale_color_manual(name = "Development",
                     labels = c("Immature","Developing","Mature"),
                     values = c("#FAB45A","#AEB4C2","#262B30"))+
    scale_shape_manual(name = "Development",
                     labels = c("Immature","Developing","Mature"),
                     values = c(15,16,17))
```


Below show boxplots comparing triploid and diploid females and associated summary statistics:

```{r}
ggplot(gonad_group, aes(y = mean_ED, x = ploidy, fill = ploidy))+
  geom_boxplot()+
  labs(x = "Ploidy)", y = "Mean Energy Density (kJ/g wet mass)")+
  theme_classic()
```

```{r}
gonad_group %>%
  group_by(ploidy) %>%
  summarize(n = n(),
            'Mean Energy Density' = mean(mean_ED),
            'SD Energy Density' = sd(mean_ED)) %>%
  knitr::kable()
```